REDUCE is an interactive system for general algebraic computations of 
interest to mathematicians, scientists and engineers. 
It has been produced by a collaborative effort involving many contributors.

REDUCE traces its origins to work begun by Anthony Hearn in 1963 and 
continued ever since. The first distribution occurred in 1968. 
Since that time, over a hundred people have been involved in various ways 
in its development.

A small number of these people have made sustained contributions to the REDUCE 
core and associated packages over many years, namely John Fitch, 
Herbert Melenk, Winfried Neun, Arthur Norman and Eberhard Schr\"ufer.


Others who have contributed to either documentation or packages for REDUCE 
include John Abbott, Paul Abbott, Victor Adamchik, Werner Antweiler, 
Alan Barnes, Andreas Bernig, Yuri A. Blinkov, Harald Boeing, W.N. Borst, 
F. Brackx, Russell Bradford, Andreas Brand, Fran Burstall, Chris Cannam, 
Hubert Caprasse, D. Constales, Caroline Cotter, James Davenport,  
Michael Dewar, C. Dicrescenzo, Andreas Dolzmann, Alain Dresse, 
Ladislav Drska, James Eastwood, Bruce A. Florman, Kerry Gaskell, 
Karin Gatermann, Barbara L. Gates, R. Gebauer, Vladimir Gerdt, 
John Gottschalk, Hans-Gert Graebe,  Martin Griss, A.G. Grozin, 
David Harper, John Harper, Steve Harrington, David Hartley, 
M.C. van Heerwaarden, Friedrich Hehl, Daniel Hobbs, Joachim Hollman, 
B.J.A. Hulshof, J.A. van Hulzen, V. Ilyin, N. Ito, F. Kako, 
Stan Kameny, C. Kazasov, Nancy Kirkwood, K. Kishimoto, Wolfram Koepf, 
H. Kredel, A.P. Kryukov, Neil Langmead, A. Lasaruk, D. Lewien, 
Richard Liska, Ruediger Loos, Malcolm MacCallum, Norman MacDonald, 
Jed Marti, Kevin McIsaac, H. Meyer, H. Michael Moeller, Mary Ann Moore, 
Shuichi Moritsugu, Donald Morrison, Alain Moussiaux, C.J. Neerdaels, 
K. Onaga, Julian Padget, Gerhard Rayna, Matt Rebbeck, Francoise Richard, 
F. Richard-Jung, A.J. Roberts, A.Ya. Rodionov, T. Sasaki, Carsten Schoebel, 
Franziska Schoebel, Rainer Schoepf, Fritz Schwarz, Andreas Seidl, 
James Sherring, Luis Alvarez Sobreviela, D. Stauffer, Gregor Stoelting, 
David R. Stoutemyer, Stephen Scowcroft, Yves Siret, M. Spiridonova, 
H. Steeb, Andreas Strotmann, Thomas Sturm, Takeyuki Takahashi, 
A. Taranov, Lisa Temme, Walter Tietze, V. Tomov, Evelyne Tournier, 
Arrigo Triulzi, R.W. Tucker, Philip A Tuckey, Gokturk Ucoluk, 
J. Ueberberg, J.B. van Veelen, Mathias Warns, Volker Winkelmann, 
Thomas Wolf, Francis Wright, K. Yamamoto, J.G. Zabolitzky, 
Alexey Yu. Zharkov and Vadim V. Zhytnikov.

and many others \ldots



